---
title: "README"
author: "Mokssh Surve"
date: "01/05/2019"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview
***
`binomial` is a minimal package in R that provides users with functions to solve and plot basic probability distributions.
The following are the functions binomial has to offer:

* `bin_choose(n, k)`  
* `bin_probability(success, trials, prob)`  
* `bin_distribution(trials, prob)`  
  + `plot.bindis()`  
* `bin_cumulative(trials, prob)`  
  + `plot.bincum()`  
* `bin_variable(trials, prob)`  
  + `print.binvar()`  
  + `summary.binvar()`  
  + `print.summary.binvar()`  
* `bin_mean()`
* `bin_variance()`
* `bin_mode()`
* `bin_skewness()`
* `bin_kurtosis()`

Note: For explanations on the purpose of each of the functions, refer to introduction.Rmd in vignettes/


## Motivation
***
This package was created as part of Workout 3 (a small project of sorts) as part of the syllabus for Stat133 offered by UC Berkeley, and taught by Professor Gaston Sanchez (& GSI Colin Kou).


## Usage
***
Note: For detailed usage examples of each function, refer to introduction.Rmd in vignettes/

```{r}
library(binomial)
library(ggplot2)

#The probability of getting 5 heads in 10 tosses of a loaded coin with 45% chance of heads:
bin_probability(success = 5, trials = 10, prob = 0.45)

#The probability distribution of successes in 10 tosses of a loaded coin with 45% chance of heads:
dist <- bin_distribution(trials = 10, prob = 0.45)
#it's plot
plot(dist)

#The cumulative probability distribution of successes in 10 tosses of a loaded coin with 45% chance of heads:
dist2 <- bin_cumulative(trials = 10, prob = 0.45)
#it's plot
plot(dist2)

#The creation of a binomial random variable and printing summary
bin1 <- bin_variable(trials = 10, p = 0.3) 
summary(bin1)

#The finding of the skewness statistic of a a binomial random variable
bin_skewness(10, 0.3)

```
